\documentclass{letter}

\usepackage[utf8]{inputenc}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{mathtools}

\begin{document}

Dear Prof.,

Please find attached the paper entitled ``Verification of an Incompressible Viscoelastic Flow Solver Using the Method of Manufactured Solutions for Oldroyd-B and Giesekus Constitutive Models", by Juniormar Organista, Leandro F. de Souza, C\'elio Fernandes, Welton L. Costa, Aquisson T. G. da Silva, Antonio Castelo. 

This paper presents a comprehensive verification methodology for a numerical code designed to simulate incompressible, two-dimensional viscoelastic fluid flows. The method employed is the Method of Manufactured Solutions (MMS). To assess the accuracy of the numerical code, we utilized the Oldroyd-B and Giesekus constitutive models to represent different viscoelastic behaviours. The code was implemented using a robust numerical framework, incorporating fourth-order compact finite difference approximations for spatial derivatives and a fourth-order Runge-Kutta scheme for time integration. A key feature of this work is the introduction of a non-stationary manufactured solution. This solution serves as a benchmark, allowing for a rigorous evaluation of the numerical code's accuracy and robustness under dynamic conditions. The proposed methodology provides a valuable tool for researchers and engineers working with viscoelastic fluid simulations, ensuring the reliability and accuracy of their numerical results. 

We shall state that this manuscript is the authors' original work and has not been published nor has it been submitted simultaneously elsewhere. All authors have checked the manuscript and have agreed to the submission.

Looking forward to hearing from you.

Best regards,

Juniormar Organista\\
Leandro F. de Souza\\
C\'elio Fernandes\\
Welton L. Costa\\
Aquisson T. G. da Silva\\
Antonio Castelo
\end{document}